---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# rTemplatePackage

<!-- badges: start -->
<!-- badges: end -->

This is a template package to show how to initiate `tests` and `vignettes`.

The file `R/examples/packageMaintenance.R` includes important functions to initiate `testing`-files, `vignettes`-files and other package stuff.

Thanks to the online book [R Packages](https://r-pkgs.org) by [Hadley Wickham](http://hadley.nz/) and [Jennifer Bryan](http://jennybryan.org/)!

## Installation

You can install the development version of rTemplatePackage from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("hatschibratschi/rTemplatePackage")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(rTemplatePackage)
hello()

```
